\thetitle

### 2021-05-14 writing/discussion.tex
fix the prose explanation of the figure

%% -----------------------------------------------------------------------------

>>>>

%% -----------------------------------------------------------------------------
% \subsection{Contextualizing the results through an example scenario}

\begin{figure}
\input{trail-example-table}
\caption{An example scenario from take5, with every mode's resulting trail.}
\label{fig:example-trails}
\end{figure}

Interpreting the numeric summaries and aggregations of the last section demands an intuitive understanding of what blame trails look like in practice.
Thus, before drawing high level conclusions, let us examine one set of scenarios with a typical debugging scenario from the {\tt take5} benchmark,
whose module dependency graph is shown in the top left of figure~\ref{fig:example-trails}.

The rest of figure~\ref{fig:example-trails} illustrates the blame trails produced by every mode of the rational programmer for the debugging scenario in
two different ways: 
\begin{itemize}

\item The top right shows the blame trails produced by every mode of the rational programmer as paths through the configuration lattice starting at the
root (leftmost) configuration. Each configuration is represented by a bit string where each digit corresponds to a module in the program and indicates if
it is typed.

\item The table in the middle expands the information in the diagram with the details of every step in each trail.
Every row of the table represents the trail of one mode. The middle-three columns depict the steps of a blame trail:
\begin{description}
\item[Root] describes the result of running the root configuration in this row's mode.
\item[Step 1] is the result of the rational programmer's reaction to the outcome of running the root. 
\item[Step 2] shows the result of reacting to the outcome of running step~1 configuration, if any. 
\end{description}
Finally, the \textbf{Success?} column summarizes whether exploring the trail succeeds.

\end{itemize}

Let us contrast rows 1 and~4. The first one shows that running the root
configuration under the Natural-blame mode fails due a dynamic type check and
blames the {\tt player} module; typing that module and running again then
results in a type error, and hence the trail is successful.  By contrast, the
Natural-exceptions mode (row 4) yields stack information for the root
configuration that is unhelpful; it identifies only {\tt main}, which is already
typed. Hence, this trail immediately gets stuck.

In short, this figure concretely demonstrates how the rational programmer
behaves in different modes. In this case, the behaviors differ from each other
in all five modes. The reader may keep these scenarios in mind as we next
discuss the numeric results of the last section.

\subsection{Interpreting the results}
